Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-15 paper/manuscript.tex
Write draft of results section 2 and figure 2 caption

\subsection*{Broad and narrow antibodies that neutralize influenza virus}
We applied this approach to several broad antibodies that neutralize the A/WSN/1933 (H1N1) influenza virus strain.
For comparison, we also included several narrow strain-specific antibodies that we have characterized previously~\cite{doud2017complete}.
Two broad anti-stalk, one all one only group 1.
One anti receptor
The narrow ones.
The last concluding sentence of your paragraph is good.

% blurbs about the specific antibodies we use here:
To quantify escape from broadly-neutralizing antibodies using the approach described above, we profiled an antibody targeting the receptor-binding site (S139/1)~\citep{yoshida2009cross, lee2012heterosubtypic}, and two antibodies targeting the stalk domain (FI6v3 and C179)~\citep{corti2011neutralizing, okuno1993common, dreyfus2013structure}. 
In addition, we included analyses of selections we previously completed with three strain-specific antibodies (H17-L19, H17-L10, and H17-L7)~\citep{doud2017complete}. 
H17-L19, H17-L10, and H17-L7 target the Ca2, Ca1, and Cb antigenic regions, respectively.
The crystal structures of the broadly-neutralizing antibodies and the binding footprints of the strain-specific antibodies are shown in Figure~\ref{fig:antibody_summary}A.
S139/1, C179, and FI6v3 also possess a wide range of breadths (Figure~\ref{fig:antibody_summary}B). 
For instance, S139/1 and FI6v3 can bind various HA's from group 1 and group 2, while C179 exhibits binding only to certain group 1 HA's.
We were therefore able to profile the ease of escape from antibodies of different specificities and breadths.

To choose appropriate concentrations of these antibodies, we performed neutralization assays using wild-type A/WSN/1933 (H1N1) virus. 
Figure~\ref{fig:neutcurves} shows the neutralization curves for each antibody, and all six antibodies show similar potencies.
We chose to conduct the library selections with concentrations of antibodies that would neutralize nearly all wildtype viruses (possibly add slightly more detail).

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/antibody_summary_fig/Ab_summary.pdf}}
\caption{\label{fig:antibody_summary}
CAPTION
}
\end{figure}

>>>>

\subsection*{Broad and narrow antibodies that neutralize influenza virus}
We applied the approach described above to several broad antibodies that neutralize the A/WSN/1933 (H1N1) influenza virus strain.
For comparison, we also included three narrow strain-specific antibodies that we previously characterized in~\cite{doud2017complete} and were used in classical antigenic mapping experiments (cite Gerhard, Caton).
The crystal structures of the broadly-neutralizing antibodies and the binding footprints of the strain-specific antibodies are shown in Figure~\ref{fig:antibody_summary}A.
Two of the broadly-neutralizing antibodies, specifically FI6v3 and C179, target the stalk domain of HA~\citep{corti2011neutralizing, okuno1993common, dreyfus2013structure}. 
However, FI6v3 exhibits binding activity across group 1 and group 2 HA's, while C179 can bind to only certain group 1 HA's (Figure~\ref{fig:antibody_summary}B).
The third broad antibody, S139/1, targets the receptor-binding site and can bind HA's from both groups~\citep{yoshida2009cross, lee2012heterosubtypic}.
The strain-specific antibodies H17-L19, H17-L10, and H17-L7 bind the Ca2, Ca1, and Cb antigenic regions, respectively.
We were therefore able to profile the ease of escape from antibodies of different specificities and breadths.

To choose appropriate concentrations of these antibodies for selection experiments, we performed neutralization assays using wildtype A/WSN/1933 (H1N1) virus. 
Figure~\ref{fig:neutcurves} shows the neutralization curves for each antibody.
All six antibodies exhibit similar potencies against the WSN virus.
We chose to conduct the library selections with concentrations of antibodies that would allow us to detect genuine escape mutants while neutralizing nearly all wildtype viruses. 
For the broad antibodies, we included multiple concentrations to impose different stringencies of selection and thereby capture escape mutations of varying effect sizes.

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/antibody_summary_fig/Ab_summary.pdf}}
\caption{\label{fig:antibody_summary}
{\bf Specificities and breadth of broad and narrow antibodies targeting influenza virus hemagglutinin.}
(A) We profiled three broadly-neutralizing and three strain-specific antibodies.
The broad antibodies are denoted by circles and the narrow antibodies are denoted by squares.
S139/1 (PDB 4GMS,~\cite{lee2012heterosubtypic}) targets the receptor-binding pocket; C179 (PDB 4HLZ,~\cite{dreyfus2013structure}) and FI6v3 (PDB 3ZTN,~\cite{corti2011neutralizing}) target the stalk. 
The crystal structures of the broad antibodies and the presumed binding footprints of the narrow antibodies~\citep{doud2017complete} are superimposed onto the structure of the HA trimer (PDB 1RVX,~\cite{gamblin2004structure}). 
(B) For each HA in the phylogenetic tree, we denote antibodies with demonstrated binding and/or neutralization activity against that HA. 
S139/1 not tested for binding against H8, H9, H11; C179 not tested for binding against H8, H11; none of the antibodies tested against H17 and H18.
}
\end{figure}
